High-Dimensional Regularized Discriminant Analysis

### 2016-12-02 reports/paper-hdrda.Rnw
Summarized timings along with bootstrap comparison

>>>>

<<munge_timing_comparisons>>=
# HDRDA vs RDA Timing Comparison Results

# Benchmarks are given in nanoseconds, which are converted to seconds
timings <- bind_rows(lapply(timing_results, as.data.frame), .id="p") %>%
  mutate(p=as.integer(p),
         expr=as.character(expr),
         Classifier=ifelse(startsWith(expr, "hdrda"), "HDRDA", "RDA"),
         Classifier=factor(Classifier),
         time=time / 1e9) %>%
  select(-expr) %>%
  filter(p %% 500 == 0) %>%
  tbl_df %>%
  group_by(p, Classifier) %>%
  mutate(wls_weights=1 / sd(time)) %>%
  ungroup

# Create DF for two facets in same plot
# First plot shows HDRDA vs RDA
# Second plot zooms in on HDRDA results
timings$Plot <- "Comparison of HDRDA and RDA"
timings_hdrda <- timings %>%
    filter(Classifier == "HDRDA") %>%
    mutate(Plot="HDRDA")
timings_combined <- bind_rows(timings, timings_hdrda)

# Build data frame to show relative timings in table
timing_ratios <- timings %>%
    group_by(p, Classifier) %>%
    summarize(median_time=median(time)) %>%
    tidyr::spread(Classifier, median_time) %>%
      mutate(ratio_time=RDA / HDRDA) %>%
      select(-HDRDA, -RDA)
@

<<bootstrap_relative_timing_comparisons>>=
ratio_means <- function(df, num_reps=1000) {
  bootstrap_reps <- replicate(n=num_reps, {
    df %>%
      group_by(Classifier) %>%
      sample_frac(size=1.0, replace=TRUE) %>%
      summarize(mean_time=mean(time)) %>%
      tidyr::spread(Classifier, mean_time) %>%
      mutate(ratio_means=RDA / HDRDA) %>%
      select(-HDRDA, -RDA)
  }, simplify=FALSE)
  bind_rows(bootstrap_reps)
}

set.seed(42)
timing_ratios_bootstrap <- timings %>%
    mutate(p=factor(p)) %>%
    group_by(p) %>%
    do(ratio_means(., num_reps=1000))

timing_bootstrap_summary <- timing_ratios_bootstrap %>%
  group_by(p) %>%
  summarize(avg_ratio=mean(ratio_means),
            lower_ci=quantile(ratio_means, probs=0.025),
            upper_ci=quantile(ratio_means, probs=0.975))
bootstrap_summary_p500 <- timing_bootstrap_summary %>%
  filter(p == "500")
bootstrap_summary_p5000 <- timing_bootstrap_summary %>%
  filter(p == "5000")

@
